Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-15 patient-clinician-workshop/pccworkshop.tex
phrs

Nonetheless, challenges abound. These primarily pertain to capturing
these activity diaries, effectively storing these diaries, and privacy
controls for giving patients the ability to disclose desired quantities
of their diary to their clinicians.  We discuss these, next.

>>>>

Nonetheless, challenges abound. These primarily pertain to capturing
these activity diaries, effectively storing these diaries, giving
users easy-to-use access to these diaries, and privacy controls for
giving patients the ability to disclose desired quantities of their
diary to their clinicians.  We discuss these, next.
